Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2024-02-14 writing/investigating-GPP.tex
updated analysis scripts

Prijection comparison hasn't been done, except in CommitmentBank paper (right?, perhaps A'dam colloquium presentation?).

@@

\begin{exe}
\exi{(3)} 
\begin{xlist}
\ex Sample control stimulus in Exps.~2n, 2m, and 2c
\begin{xlist}
\exi{A:} These muffins, which are really delicious, have blueberries in them.
\exi{B:} Yes, that's true, they have blueberries in them.
\end{xlist}
Question to participants: Does A's response to B sound good?
\ex Sample control stimulus in Exp.~2q
\begin{xlist}
\exi{A:} Do these muffins, which are really delicious, have blueberries in them?
\exi{B:} Yes, they have blueberries in them.
\end{xlist}
Question to participants: Does A's response to B sound good?
\end{xlist}
\end{exe}
As shown in Table \ref{t-controls},  the group mean on the control stimuli is numerically higher (at .22 or .25) than for Exp.~2q (.07). We hypothesize that a possible explanation for this difference is that participants take A to assert both the content of the main clause and of the NRRC in (3a) but is only asking about the main clause content in (3b). Whereas B's affirmation in (3b) specifies the one content that is affirmed, B's assent in (3a) specifies only one of the two contents that A asserted, seemingly leaving out a specification of the second content, that of the NRRC. Participants may judge B's response in (3b) to be less acceptable than in (3a) because of this missing content specification. This hypothesis is consistent with the results of \citepos{syrett-koev2015} Exp.~3, which suggests that content of a sentence-medial NRRCs can be the target of a direct denial, though the main clause content is preferred as the target of such a denial. That the group means on the control stimuli in our Exps.~2n, 2m, and 2c are still relatively low may be due to the fact that the one content that was specified is the at-issue main clause content. One would expect lower acceptability ratings in a version of this diagnostic in which the one content that was specified is the NRRC.

@@

\begin{exe}
\exi{(4)} 
\begin{xlist}
\ex Sample control stimulus in Exp.~3q
\begin{xlist}
\exi{A:} Do these muffins, which are really delicious, have blueberries in them?
\exi{B:} Yes, but they aren't really delicious.
\end{xlist}
Question to participants: Does A's response to B sound good?
\ex Sample control stimulus in Exps.~3n, 3m, and 3c
\begin{xlist}
\exi{A:} These muffins, which are really delicious, have blueberries in them.
\exi{B:} Yes, that's true, they but they aren't really delicious.
\end{xlist}
Question to participants: Does A's response to B sound good?
\end{xlist}
\end{exe}
The mean at-issueness rating for the control stimuli in Exp.~3q was comparatively higher (at .28) than for Exp.~1q (.05) or Exp.~2q (.07). We hypothesize that that this difference (especially to Exp.~2q) is due the content of the NRRC being directly denied, even though it was presented as backgrounded content in A's question (as shown in (2), the content of none of the other NRRCs was a matter of personal taste).

>>>>

Projection comparison hasn't been done, except in CommitmentBank paper (right?, perhaps A'dam colloquium presentation?).

@@

  \begin{exe}
  \exi{(3)} 
  \begin{xlist}
  \ex Sample control stimulus in Exps.~2n, 2m, and 2c
  \begin{xlist}
  \exi{A:} These muffins, which are really delicious, have blueberries in them.
  \exi{B:} Yes, that's true, they have blueberries in them.
  \end{xlist}
  Question to participants: Does A's response to B sound good?
  \ex Sample control stimulus in Exp.~2q
  \begin{xlist}
  \exi{A:} Do these muffins, which are really delicious, have blueberries in them?
  \exi{B:} Yes, they have blueberries in them.
  \end{xlist}
  Question to participants: Does A's response to B sound good?
  \end{xlist}
  \end{exe}

  As shown in Table \ref{t-controls},  the group mean on the control stimuli is numerically higher (at .22 or .25) than for Exp.~2q (.07). We hypothesize that a possible explanation for this difference is that participants take A to assert both the content of the main clause and of the NRRC in (3a) but is only asking about the main clause content in (3b). Whereas B's affirmation in (3b) specifies the one content that is affirmed, B's assent in (3a) specifies only one of the two contents that A asserted, seemingly leaving out a specification of the second content, that of the NRRC. Participants may judge B's response in (3b) to be less acceptable than in (3a) because of this missing content specification. This hypothesis is consistent with the results of \citepos{syrett-koev2015} Exp.~3, which suggests that content of a sentence-medial NRRCs can be the target of a direct denial, though the main clause content is preferred as the target of such a denial. That the group means on the control stimuli in our Exps.~2n, 2m, and 2c are still relatively low may be due to the fact that the one content that was specified is the at-issue main clause content. One would expect lower acceptability ratings in a version of this diagnostic in which the one content that was specified is the NRRC.

@@

  \begin{exe}
  \exi{(4)} 
  \begin{xlist}
  \ex Sample control stimulus in Exp.~3q
  \begin{xlist}
  \exi{A:} Do these muffins, which are really delicious, have blueberries in them?
  \exi{B:} Yes, but they aren't really delicious.
  \end{xlist}
  Question to participants: Does A's response to B sound good?
  \ex Sample control stimulus in Exps.~3n, 3m, and 3c
  \begin{xlist}
  \exi{A:} These muffins, which are really delicious, have blueberries in them.
  \exi{B:} Yes, that's true, they but they aren't really delicious.
  \end{xlist}
  Question to participants: Does A's response to B sound good?
  \end{xlist}
  \end{exe}

  The mean at-issueness rating for the control stimuli in Exp.~3q was comparatively higher (at .28) than for Exp.~1q (.05) or Exp.~2q (.07). We hypothesize that that this difference (especially to Exp.~2q) is due the content of the NRRC being directly denied, even though it was presented as backgrounded content in A's question (as shown in (2), the content of none of the other NRRCs was a matter of personal taste).
